
\addcontentsline{toc}{chapter}{Bibliography}
\begin{thebibliography}{1}

% ha-schema

\bibitem[HANC]{HAClusterNodeConfigurations} High Availability Cluster - Node configurations - Wikipedia Article
\url{http://en.wikipedia.org/wiki/High-availability_cluster#Node_configurations}. Last access 2013-09-12.

% problem-description

\bibitem[WIHA]{WikipediaHA} High Availability Wikipedia Article
\url{http://en.wikipedia.org/wiki/High_availability}. Last access 2013-08-20.

\bibitem[ATFC]{TaskForceHA} IEEE Task Force on Cluster Computing. archive.org capture from February 2011.
\url{http://web.archive.org/web/20110216113021/http://www.ieeetfcc.org/high-availability.html}. Last access 2013-08-20.

\bibitem[BCHA]{BCMHA} High Availability Bcmpedia definition
\url{http://www.bcmpedia.org/wiki/High_Availability}. Last access 2013-08-20.

\bibitem[ZLEA]{ZimbraLearn} Zimbra - Learn
\url{http://www.zimbra.com/learn/}. Last access 2013-08-20.

\bibitem[VWZ8]{VmwareZimbra8Announce} Zimbra Blog - Announcing The General Availability of Zimbra 8
\url{http://blog.zimbra.com/blog/archives/2012/09/announcing-the-general-availability-of-zimbra-8.html}. Last access 2013-08-20.

% operating-system-installation

\bibitem[UWHA]{UbuntuWhatIs} Ubuntu Official Documentation - What is Ubuntu?
\url{https://help.ubuntu.com/lts/installation-guide/amd64/what-is-ubuntu.html}. Last access 2013-09-11.

\bibitem[UMIN]{UbuntuMinimalDisk} Ubuntu Community Help Wiki - Installation - MinimalCD
\url{https://help.ubuntu.com/community/Installation/MinimalCD}. Last access 2013-08-20.

\bibitem[LDIN]{LinbitDRBDInternals} LinBit DRBD version 8.4 Guide - Chapter 17 . DRBD Internals
\url{http://www.drbd.org/users-guide/ch-internals.html}. Last access 2013-08-20.

% network-setup

\bibitem[ZWPO]{ZimbraWikiPorts} Zimbra Wiki - Ports
\url{http://wiki.zimbra.com/wiki/Ports}. Last access 2013-09-06.

% zimbra-installation

\bibitem[ZWWW]{ZimbraWeb} Zimbra - Official web page
\url{http://www.zimbra.com}. Last access 2013-09-11.

\bibitem[VWZD]{Zimbra8Download} Zimbra - Open Source Edition Downloads
\url{http://www.zimbra.com/downloads/os-downloads.html}. Last access 2013-08-20.

\bibitem[ZPTG]{ZimbraPerformanceTuning} Zimbra Wiki - Performance Tuning Guidelines for Large Deployments
\url{http://wiki.zimbra.com/wiki/Performance_Tuning_Guidelines_for_Large_Deployments}. Last access 2013-09-12.

% drbd-setup

\bibitem[LDWI]{LinbitDRBDWhatIs} Linbit DRBD - What is DRBD
\url{http://www.drbd.org/home/what-is-drbd/}. Last access 2013-08-20.

\bibitem[LDDC]{LinbitDRBDdrbdconf} drbd.conf — Configuration file for DRBD\'s devices
\url{http://www.drbd.org/users-guide/re-drbdconf.html}. Last access 2013-08-20.

% corosync-pacemaker-installation

\bibitem[WCSA]{WikipediaCorosync} Corosync project Wikipedia Article
\url{http://en.wikipedia.org/wiki/Corosync_(project)}. Last access 2013-08-20.

\bibitem[CORW]{CorosyncWebpage} Corosync web page
\url{http://corosync.github.io/corosync/}. Last access 2013-08-20.

\bibitem[CLPW]{PacemakerWebpage} Cluster Labs - The Home of Pacemaker
\url{http://clusterlabs.org/}. Last access 2013-08-20.

% initial-pacemaker-setup

\bibitem[LHRA]{ResourceAgentsWiki} Linux High Availability Wiki - Resource Agents
\url{http://linux-ha.org/wiki/Resource_Agents}. Last access 2013-08-20.

\bibitem[LORA]{OCFResourceAgentsWiki} Linux High Availability Wiki - OCF Resource Agents
\url{http://linux-ha.org/wiki/OCF_Resource_Agents}. Last access 2013-08-20.

\bibitem[BTAO]{BtacticOrg} Btactic Org web page
\url{http://www.btactic.org}. Last access 2013-08-20.

\bibitem[BTOC]{BtacticOCF} Btactic OCF Resource Agents for High Availability Version 0.02
\url{http://www.btactic.org/btactic_ocf_0.0.2.tar.gz}. Last access 2013-08-20.

% pacemaker-final-setup

\bibitem[PMCS]{ClustersFromScratch} Pacemaker 1.1 for Corosync 2.x and crmsh - Cluster from Scratch
\url{http://clusterlabs.org/doc/en-US/Pacemaker/1.1-crmsh/html/Clusters_from_Scratch/index.html}. Last access 2013-08-20.

% ha-system-management

\bibitem[ZFTA]{ZForumsTaer} Zimbra Forums - Zimbra on Pacemaker + DRBD howto - Page 2
\url{http://www.zimbra.com/forums/administrators/58113-zimbra-pacemaker-drbd-howto-2.html#post251023}. Last access 2013-08-20.

\bibitem[HAZ8]{TaerHowtoHAZimbra8} How-to HA with Zimbra OSE
\url{https://www.dropbox.com/s/8w4f7koz9ym3cle/Howto_HA_Zimbra8.pdf}. Last access 2013-08-20.

\bibitem[DSBN]{DrbdSplitBrain} Split brain notification and automatic recovery
\url{http://www.drbd.org/users-guide-8.3/s-split-brain-notification-and-recovery.html}. Last access 2013-09-08.

% improvements

\bibitem[LHFE]{LinuxHAFencing} Linux High Availability Wiki - Fencing Article
\url{http://linux-ha.org/wiki/Fencing}. Last access 2013-08-20.

\bibitem[LHST]{LinuxHAStonith} Linux High Availability Wiki - Stonith Article
\url{http://linux-ha.org/wiki/STONITH}. Last access 2013-08-20.

\bibitem[LCML]{LinuxClusterML201307} [Linux-cluster] fence-agents-4.0.2 stable release
\url{http://www.redhat.com/archives/linux-cluster/2013-July/msg00028.html}. Last access 2013-08-20.

\bibitem[ZPAO]{ZimbraProjectAlwaysOn} Zimbra Blog - Project Always On
\url{http://blog.zimbra.com/blog/archives/2013/09/project-always-on.html}. Last access 2013-09-12.


\end{thebibliography}

